Scalar and Representative Observables, and Their Associated Statistial Model, for Polarimetric SAR Data

### 2013-11-11 Remote_Sensing_Letter/paper.tex
updated prof Vun's changes

\begin{abstract}
%Problem statement  
This paper proposes scalar and representative observables for multi-dimensional POLSAR data,
  which includes several statistically consistent discrimination measures. %can be derived.
%What actually were done? and As the result, what is learned?
Specifically, the statistical behaviour of the POLSAR covariance matrix determinant is used
  to derive a scalar and generic statistical model for multi-dimensional POLSAR data,
  which is shown applicable to the two and three dimensional versions of partial and full monostatic polarimetric SAR data.
As the POLSAR covariance matrix determinant generalizes the SAR intensity towards multiple dimensions,
  the proposed model is able to subsume the traditional SAR intensity model under the umbrella of a unified model. 
%What are the larger implications of the findings presented in this paper?
Consequently, the main beneficial implications are that %of the proposed approach is that
  it provides a consistent theory unifying the currently disconnected proposals for SAR and POLSAR discrimination measures,
  and it simplifies the adaptation of existing SAR data processing techniques for POLSAR data.
%  it enables the adaptation of many existing SAR data processing techniques for POLSAR data,
%  and at the same time, it provides a consistent theory unifying the seemingly disparate discrimination measure proposals for SAR and POLSAR data.
\end{abstract}

@@

%Research Objective: Give your precise problem statement  
This paper presents scalar and representative observables,
  and one associated generic statistical model,
  that describe multi-dimensional POLSAR data and provide a consistent foundation for the derivation of discrimination measures.
%Now State your approach  
%This study started off with the observation that the determinant of the covariance matrix is widely used in POLSAR discrimination measures.
%However, our survey of existing scalar models for POLSAR indicates that no statistical model for this observable has been published so far.
%Consequently, in this article, the statistical behaviour of the determinant of POLSAR covariance matrix is further investigated.
%Prof Vuns: comment: the article provides the result, not the journey!
%Specifically POLSAR data have been statistically modelled as following the complex Wishart distribution.
The development is based on the common assumption that POLSAR data follows the complex Wishart distribution.  
Subsquently, the generic statistical model for the covariance matrix determinant is presented as being just a scalar projection of the multidimensional data.
This model is then used to derive several scalar and consistent statistical distribution suggesting that their associated observables are capable of being used as discrimination measures for POLSAR.
%
%***IVM: the following sentence doesn't make sense, also, I don't think it's good to talk about 'models of a model'.  Maybe 'model variants' instead?
%%%***IVM***The specific two and three dimensional models of these models, which %also include the derived discrimination measures, are originally designed against both partial and full polarimetric SAR data.

>>>>

\begin{abstract}
%Problem statement
This paper proposes scalar and representative observables,
  including several statistically consistent discrimination measure
  that are vitally important in the processing of multi-dimensional POLSAR data.
%This paper proposes scalar and representative observables for multi-dimensional POLSAR data,
%  which includes several statistically consistent discrimination measures. %can be derived.
%What actually were done? and As the result, what is learned?
Specifically, the statistical behaviour of the POLSAR covariance matrix determinant is used
  to derive a scalar and generic statistical model for multi-dimensional POLSAR data,
  which is shown applicable to the two and three dimensional versions of partial and full monostatic polarimetric SAR data.
As the POLSAR covariance matrix determinant generalizes the SAR intensity towards multiple dimensions,
  the proposed model is able to subsume the traditional SAR intensity model under the umbrella of a unified model. 
%What are the larger implications of the findings presented in this paper?
Consequently, the main beneficial implications are that %of the proposed approach is that
  it provides a consistent theory unifying the currently disconnected proposals for SAR and POLSAR discrimination measures,
  and it simplifies the adaptation of existing SAR data processing techniques for POLSAR data.
%  it enables the adaptation of many existing SAR data processing techniques for POLSAR data,
%  and at the same time, it provides a consistent theory unifying the seemingly disparate discrimination measure proposals for SAR and POLSAR data.
\end{abstract}

@@

%Research Objective: Give your precise problem statement  
This paper presents scalar and representative observables,
  and one associated generic statistical model,
  that describe multi-dimensional POLSAR data and provide a consistent foundation for the derivation of discrimination measures.
%Now State your approach  
%This study started off with the observation that the determinant of the covariance matrix is widely used in POLSAR discrimination measures.
%However, our survey of existing scalar models for POLSAR indicates that no statistical model for this observable has been published so far.
%Consequently, in this article, the statistical behaviour of the determinant of POLSAR covariance matrix is further investigated.
%Prof Vuns: comment: the article provides the result, not the journey!
%Specifically POLSAR data have been statistically modelled as following the complex Wishart distribution.
The development is based on the common assumption that POLSAR data follows the complex Wishart distribution.  
Subsquently, the generic statistical model for the covariance matrix determinant is presented as being just a scalar projection of the multidimensional data.
This model is then used to derive several scalar and consistent statistical distributions suggesting that their associated observables are capable of being used as discrimination measures for POLSAR.
%
%***IVM: the following sentence doesn't make sense, also, I don't think it's good to talk about 'models of a model'.  Maybe 'model variants' instead?
%%%***IVM***The specific two and three dimensional models of these models, which %also include the derived discrimination measures, are originally designed against both partial and full polarimetric SAR data.
